Supplement to: Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 supplement.tex
beef up end of supplement

\subsection{List Functions}
The lower section with seven primitives designates those given to the
\emph{rich} DSL variant and not the \emph{base} variant. The rich variant is
not supplied the \texttt{if} primitive, because its primary intention is to
enable the learning of the lower five concepts.
Greek letters represent polymorphic types.
\begin{center}
\tt
\begin{tabular}{| l | l |}
  \hline
  \textrm{\emph{name}} & \textrm{\emph{type}} \\
  \hline
    empty & $\left[\alpha\right]$ \\
    singleton & $\alpha \to \left[\alpha\right]$ \\
    concat & $\left[\alpha\right] \to \left[\alpha\right] \to \left[\alpha\right]$ \\
    mapi & $(\mathbb{Z} \to \alpha \to \beta)$ \\
    & \qquad\qquad$\to \left[\alpha\right] \to \left[\beta\right]$ \\
    reducei & $(\beta \to \mathbb{Z} \to \alpha \to \beta)$\\
    & \qquad\qquad$\to \beta \to \left[\alpha\right] \to \beta$ \\
    \hline
    if & bool $\to \alpha \to \alpha \to \alpha$ \\
    \hline
    true & bool \\
    not & bool $\to$ bool \\
%UNUSED+UNNECESSARY:    and & bool $\to$ bool $\to$ bool \\
%UNUSED+UNNECESSARY:    or & bool $\to$ bool $\to$ bool \\
    0 $\cdots$ 5 & $\mathbb{Z}$ \\
    + & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    * & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    negate & $\mathbb{Z} \to \mathbb{Z}$ \\
    mod & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    eq? & $\mathbb{Z} \to \mathbb{Z} \to$ bool \\
    gt? & $\mathbb{Z} \to \mathbb{Z} \to$ bool \\
    is-prime & $\mathbb{Z} \to$ bool \\
    is-square & $\mathbb{Z} \to$ bool \\
    range & $\mathbb{Z} \to$ [$\mathbb{Z}$] \\
    sort & $\left[\mathbb{Z}\right] \to \left[\mathbb{Z}\right]$ \\
    \hline
    sum & $\left[\mathbb{Z}\right] \to \mathbb{Z}$ \\
    reverse & $\left[\alpha\right] \to \left[\alpha\right]$ \\
    all & $(\alpha \to$ bool$) \to \left[\alpha\right] \to$ bool \\
    any & $(\alpha \to$ bool$) \to \left[\alpha\right] \to$ bool \\
    index & $\mathbb{Z} \to \left[\alpha\right] \to \alpha$ \\
    filter & $(\alpha \to$ bool$) \to \left[\alpha\right] \to \left[\alpha\right]$ \\
    slice & $\mathbb{Z} \to \mathbb{Z} \to \left[\alpha\right] \to \left[\alpha\right]$ \\
  \hline
\end{tabular}
\end{center}
  \end{comment}
\vfill

@@

Here we present representative DSLs learned by
our model. DSL primitives discovered by the algorithm are prefixed with
\lstinline!#!.
Variables are prefixed with \lstinline!$!, and we use De Bruijn indices to model variables~\cite{pierce}.
We abbreviate lambda as \lstinline!\!.

@@

\subsection{List functions}
\begin{lstlisting}
#(\ (\ (index $0 (sort $1))))
#(\ (\ (slice $0 (+ $1 4))))
#(mapi (\ (\ (eq? $0 $2))))
#(\ (mapi (\ (\ (gt? $0 $2)))))
#(\ (any (\ (eq? $0 $1))))
#(\ (mapi (\ (\ (+ $0 $2)))))
#(\ (\ (mapi (\ (\ (index $2 $3))) $1)))
#(\ (mapi (\ (\ (mod $0 $2)))))
#(\ (mapi (\ (\ (* $0 $2)))))
#(\ (\ (singleton (index $0 $1))))
#(\ (\ (slice $0 (sum $1) $1)))
#(slice 0)
#(\ (\ (index (negate $0) (sort $1))))
#(\ (++ (singleton $0)))
#(\ (\ (++ $0 (singleton $1))))
#(\ (\ (++ $0 (singleton (index $1 $0)))))
#(\ (\ (++ (singleton (index $0 $1)) $1)))
#(\ (\ (\ (#(\ (mapi (\ (\ (mod $0 $2))))) $0 (#(\ (mapi (\ (\ (+ $0 $2))))) $1 $2)))))
#(\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))
#(#(\ (mapi (\ (\ (gt? $0 $2))))) 3 empty)
#(all (\ (is-square $0)))
#(\ (\ (#(\ (mapi (\ (\ (mod $0 $2))))) $0 (#(\ (mapi (\ (\ (+ $0 $2))))) 1 $1))))
#(\ (\ (all (\ $0) (#(\ (\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))) $0 $1))))
#(\ (all (\ $0) (#(\ (\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))) $0 2)))
#(filter (\ (#(\ (all (\ $0) (#(\ (\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))) $0 2))) (singleton $0))))
#(\ (\ (\ (++ (#(slice 0) $0 $1) (#(\ (\ (slice $0 (sum $1) $1))) $1 $2)))))
#(\ (filter (\ (#(\ (\ (all (\ $0) (#(\ (\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))) $0 $1)))) $1 (singleton $0)))))
#(filter (\ (not (#(\ (all (\ $0) (#(\ (\ (#(\ (mapi (\ (\ (eq? $0 $2))))) 0 (#(\ (mapi (\ (\ (mod $0 $2))))) $0 $1)))) $0 2))) (singleton $0)))))
#(\ (++ $0 (++ $0 $0)))
#(\ (++ $0 (#(\ (++ $0 (++ $0 $0))) $0)))
#(index 0)
\end{lstlisting}

\subsection{Text editing}
\begin{lstlisting}
#(\ (\ (fold $0 $0 (\ (\ (if (char-eq? $1 $3) empty (cons $1 $0)))))))
#(\ (\ (fold $0 $1 (\ (\ (cons $1 $0))))))
#(\ (\ (fold $0 $0 (\ (\ (cdr (if (char-eq? $1 $3) $2 $0)))))))
#(\ (\ (#(\ (\ (fold $0 $1 (\ (\ (cons $1 $0)))))) (cons $0 $1))))
#(\ (\ (fold $0 $0 (\ (\ (fold $0 $0 (\ (\ (if (char-eq? $1 $5) (cdr $2) $0)))))))))
#(\ (#(\ (\ (\ (cons (car $0) (cons $1 $2))))) (#(#(\ (\ (\ (cons (car $0) (cons $1 $2))))) empty) '.' $0) '.'))
#(\ (\ (map (\ (if (char-eq? $1 $0) $2 $0)))))
#(\ (map (\ (index $0 $1))))
#(\ (unfold $0 (\ (empty? $0)) (\ (car $0)) (\ (#(\ (\ (fold $0 $0 (\ (\ (cdr (if (char-eq? $1 $3) $2 $0))))))) SPACE $0))))
#(#(\ (\ (\ (cons (car $0) (cons $1 $2))))) empty)
\end{lstlisting}

\subsection{Symbolic regression}
\begin{lstlisting}
#(\ (#(\ (+. $0 REAL)) (*. $0 REAL)))
#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0)))
#(\ (#(\ (+. $0 REAL)) (*. (#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0))) $0) $0)))
#(\ (#(/. REAL) (#(\ (+. $0 REAL)) $0)))
#(/. REAL)
#(\ (/. (/. REAL $0) $0))
#(\ (+. $0 REAL))
#(\ (#(\ (+. $0 REAL)) (*. $0 (#(\ (#(\ (+. $0 REAL)) (*. (#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0))) $0) $0))) $0))))
#(\ (/. (#(\ (/. (/. REAL $0) $0)) $0) $0))
#(\ (\ (#(/. REAL) (/. (#(\ (+. $0 REAL)) $0) $1))))
#(\ (#(\ (+. $0 REAL)) (#(\ (#(/. REAL) (#(\ (+. $0 REAL)) $0))) $0)))
#(#(\ (\ (#(/. REAL) (/. (#(\ (+. $0 REAL)) $0) $1)))) (#(\ (/. (#(\ (/. (/. REAL $0) $0)) $0) $0)) REAL))
#(\ (/. (#(\ (#(\ (#(\ (+. $0 REAL)) (*. $0 REAL))) (*. (#(\ (+. $0 REAL)) $0) $0))) $0) (#(\ (+. $0 REAL)) $0)))
\end{lstlisting}

>>>>

\subsection{List Functions}
The lower section with seven primitives designates those given to the
\emph{rich} DSL variant and not the \emph{base} variant. The rich variant is
not supplied the \texttt{if} primitive, because its primary intention is to
enable the learning of the lower five concepts.
Greek letters represent polymorphic types.
\begin{center}
\tt
\begin{tabular}{| l | l |}
  \hline
  \textrm{\emph{name}} & \textrm{\emph{type}} \\
  \hline
    empty & $\left[\alpha\right]$ \\
    singleton & $\alpha \to \left[\alpha\right]$ \\
    concat & $\left[\alpha\right] \to \left[\alpha\right] \to \left[\alpha\right]$ \\
    mapi & $(\mathbb{Z} \to \alpha \to \beta)$ \\
    & \qquad\qquad$\to \left[\alpha\right] \to \left[\beta\right]$ \\
    reducei & $(\beta \to \mathbb{Z} \to \alpha \to \beta)$\\
    & \qquad\qquad$\to \beta \to \left[\alpha\right] \to \beta$ \\
    \hline
    if & bool $\to \alpha \to \alpha \to \alpha$ \\
    \hline
    true & bool \\
    not & bool $\to$ bool \\
%UNUSED+UNNECESSARY:    and & bool $\to$ bool $\to$ bool \\
%UNUSED+UNNECESSARY:    or & bool $\to$ bool $\to$ bool \\
    0 $\cdots$ 5 & $\mathbb{Z}$ \\
    + & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    * & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    negate & $\mathbb{Z} \to \mathbb{Z}$ \\
    mod & $\mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ \\
    eq? & $\mathbb{Z} \to \mathbb{Z} \to$ bool \\
    gt? & $\mathbb{Z} \to \mathbb{Z} \to$ bool \\
    is-prime & $\mathbb{Z} \to$ bool \\
    is-square & $\mathbb{Z} \to$ bool \\
    range & $\mathbb{Z} \to$ [$\mathbb{Z}$] \\
    sort & $\left[\mathbb{Z}\right] \to \left[\mathbb{Z}\right]$ \\
    \hline
    sum & $\left[\mathbb{Z}\right] \to \mathbb{Z}$ \\
    reverse & $\left[\alpha\right] \to \left[\alpha\right]$ \\
    all & $(\alpha \to$ bool$) \to \left[\alpha\right] \to$ bool \\
    any & $(\alpha \to$ bool$) \to \left[\alpha\right] \to$ bool \\
    index & $\mathbb{Z} \to \left[\alpha\right] \to \alpha$ \\
    filter & $(\alpha \to$ bool$) \to \left[\alpha\right] \to \left[\alpha\right]$ \\
    slice & $\mathbb{Z} \to \mathbb{Z} \to \left[\alpha\right] \to \left[\alpha\right]$ \\
  \hline
\end{tabular}
\end{center}
  \end{comment}

@@

Here we present representative DSLs learned by our model. DSL primitives
discovered by the algorithm are prefixed with \lstinline!#!.
Variables are prefixed with \lstinline!$!, and we adopt De Bruijn indices to
model bound variables~\cite{pierce}.

@@

\lstset{escapechar=@}
\subsection{List functions}
\begin{lstlisting}
#(+ 1 1)
#(@$\lambda$@ (cdr (cdr $0)))
#(@$\lambda$@ (fold $0 1 (@$\lambda$@ (@$\lambda$@ (* $0 $1)))))
#(@$\lambda$@ (cons (car $0) empty))
#(@$\lambda$@ (@$\lambda$@ (fold $0 $1 (@$\lambda$@ (@$\lambda$@ (cons $1 $0))))))
#(@$\lambda$@ (@$\lambda$@ (fold $0 (empty? $0) (@$\lambda$@ (@$\lambda$@ (if $0 $0 (eq? $3 $1)))))))
#(@$\lambda$@ (map (@$\lambda$@ (eq? $1 $0))))
#(@$\lambda$@ (* $0 (* $0 $0)))
#(+ 1 #(+ 1 1))
#(@$\lambda$@ (map (@$\lambda$@ (gt? $0 $1))))
#(@$\lambda$@ (fold $0 empty (@$\lambda$@ (@$\lambda$@ (if (is-square $1) (cons $1 $0) $0)))))
#(@$\lambda$@ (map (@$\lambda$@ (eq? $0 (length (range $0)))) $0))
#(@$\lambda$@ (@$\lambda$@ (map (@$\lambda$@ (index $0 $1)) (range $1))))
#(@$\lambda$@ (cdr (#(@$\lambda$@ (cdr (cdr $0))) $0)))
#(@$\lambda$@ (map (@$\lambda$@ (index 1 $1))))
#(@$\lambda$@ (fold $0 empty (@$\lambda$@ (@$\lambda$@ (cons $1 (cons $1 $0))))))
#(@$\lambda$@ (@$\lambda$@ (cons (car $0) $1)))
#(+ 1 #(+ 1 #(+ 1 1)))
#(@$\lambda$@ (map (@$\lambda$@ (gt? 1 (mod $0 $1)))))
#(@$\lambda$@ (@$\lambda$@ (map (@$\lambda$@ (mod (+ $0 $1) $2)))))
#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (fold $0 $1 (@$\lambda$@ (@$\lambda$@ (cons $1 $0)))))) (#(@$\lambda$@ (@$\lambda$@ (fold $0 $1 (@$\lambda$@ (@$\lambda$@ (cons $1 $0)))))) $0 $0) $0))
#(@$\lambda$@ (@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (fold $0 $1 (@$\lambda$@ (@$\lambda$@ (cons $1 $0)))))) (cons $0 empty) $1)))
#(+ #(+ 1 #(+ 1 1)) #(+ 1 1))
#(@$\lambda$@ (map (@$\lambda$@ (+ #(+ 1 #(+ 1 1)) (+ $1 $0)))))
#(@$\lambda$@ (map (@$\lambda$@ (+ $0 $1))))
#(@$\lambda$@ (@$\lambda$@ (fold $0 (empty? $0) (@$\lambda$@ (@$\lambda$@ (gt? $1 (#(@$\lambda$@ (* $0 (* $0 $0))) $3)))))))
#(@$\lambda$@ (fold $0 0 (@$\lambda$@ (@$\lambda$@ (+ $0 (#(@$\lambda$@ (fold $0 1 (@$\lambda$@ (@$\lambda$@ (* $0 $1))))) (range $1)))))))
#(@$\lambda$@ (#(@$\lambda$@ (cdr (#(@$\lambda$@ (cdr (cdr $0))) $0))) (cdr $0)))
#(@$\lambda$@ (#(@$\lambda$@ (fold $0 empty (@$\lambda$@ (@$\lambda$@ (if (is-square $1) (cons $1 $0) $0))))) (map (@$\lambda$@ (* $0 (+ $0 $0))) $0)))
#(@$\lambda$@ (@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (fold $0 $1 (@$\lambda$@ (@$\lambda$@ (cons $1 $0)))))) (#(@$\lambda$@ (cons (car $0) empty)) $0) $1)))
#(@$\lambda$@ (@$\lambda$@ (length (#(@$\lambda$@ (#(@$\lambda$@ (fold $0 empty (@$\lambda$@ (@$\lambda$@ (if (is-square $1) (cons $1 $0) $0))))) (map (@$\lambda$@ (* $0 (+ $0 $0))) $0))) (map (@$\lambda$@ (- $1 $0)) $1)))))
#(@$\lambda$@ (@$\lambda$@ (is-square (#(@$\lambda$@ (fold $0 1 (@$\lambda$@ (@$\lambda$@ (* $0 $1))))) (#(@$\lambda$@ (@$\lambda$@ (map (@$\lambda$@ (mod (+ $0 $1) $2))))) (length (#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (fold $0 $1 (@$\lambda$@ (@$\lambda$@ (cons $1 $0)))))) (#(@$\lambda$@ (@$\lambda$@ (fold $0 $1 (@$\lambda$@ (@$\lambda$@ (cons $1 $0)))))) $0 $0) $0)) $0)) $1 $0)))))
#(@$\lambda$@ (@$\lambda$@ (fold (cdr $0) $1 (@$\lambda$@ (@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (fold $0 $1 (@$\lambda$@ (@$\lambda$@ (cons $1 $0)))))) (#(@$\lambda$@ (cons (car $0) empty)) $0) $1))) (cdr $0) $0))))))
#(@$\lambda$@ (empty? (#(@$\lambda$@ (#(@$\lambda$@ (fold $0 empty (@$\lambda$@ (@$\lambda$@ (if (is-square $1) (cons $1 $0) $0))))) (map (@$\lambda$@ (* $0 (+ $0 $0))) $0))) (#(@$\lambda$@ (@$\lambda$@ (map (@$\lambda$@ (mod (+ $0 $1) $2))))) #(+ 1 1) 1 $0))))
#(@$\lambda$@ (@$\lambda$@ (gt? (#(@$\lambda$@ (@$\lambda$@ (length (#(@$\lambda$@ (#(@$\lambda$@ (fold $0 empty (@$\lambda$@ (@$\lambda$@ (if (is-square $1) (cons $1 $0) $0))))) (map (@$\lambda$@ (* $0 (+ $0 $0))) $0))) (map (@$\lambda$@ (- $1 $0)) $1))))) $0 $1) 1)))
\end{lstlisting}

\subsection{Text editing}
\begin{lstlisting}
#(@$\lambda$@ (@$\lambda$@ (fold $0 $0 (@$\lambda$@ (@$\lambda$@ (if (char-eq? $1 $3) empty (cons $1 $0)))))))
#(@$\lambda$@ (@$\lambda$@ (fold $0 $1 (@$\lambda$@ (@$\lambda$@ (cons $1 $0))))))
#(@$\lambda$@ (@$\lambda$@ (fold $0 $0 (@$\lambda$@ (@$\lambda$@ (cdr (if (char-eq? $1 $3) $2 $0)))))))
#(@$\lambda$@ (@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (fold $0 $1 (@$\lambda$@ (@$\lambda$@ (cons $1 $0)))))) (cons $0 $1))))
#(@$\lambda$@ (@$\lambda$@ (fold $0 $0 (@$\lambda$@ (@$\lambda$@ (fold $0 $0 (@$\lambda$@ (@$\lambda$@ (if (char-eq? $1 $5) (cdr $2) $0)))))))))
#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (cons (car $0) (cons $1 $2))))) (#(#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (cons (car $0) (cons $1 $2))))) empty) '.' $0) '.'))
#(@$\lambda$@ (@$\lambda$@ (map (@$\lambda$@ (if (char-eq? $1 $0) $2 $0)))))
#(@$\lambda$@ (map (@$\lambda$@ (index $0 $1))))
#(@$\lambda$@ (unfold $0 (@$\lambda$@ (empty? $0)) (@$\lambda$@ (car $0)) (@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (fold $0 $0 (@$\lambda$@ (@$\lambda$@ (cdr (if (char-eq? $1 $3) $2 $0))))))) SPACE $0))))
#(#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (cons (car $0) (cons $1 $2))))) empty)
\end{lstlisting}

\subsection{Symbolic regression}
\begin{lstlisting}
#(@$\lambda$@ (/. (/. REAL $0) $0))
#(@$\lambda$@ (+. $0 REAL))
#(@$\lambda$@ (#(@$\lambda$@ (+. $0 REAL)) (*. $0 (#(@$\lambda$@ (#(@$\lambda$@ (+. $0 REAL)) (*. (#(@$\lambda$@ (#(@$\lambda$@ (#(@$\lambda$@ (+.  $0 REAL)) (*. $0 REAL))) (*. (#(@$\lambda$@ (+. $0 REAL)) $0) $0))) $0) $0))) $0))))
#(@$\lambda$@ (/. (#(@$\lambda$@ (/. (/. REAL $0) $0)) $0) $0))
#(@$\lambda$@ (@$\lambda$@ (#(/. REAL) (/. (#(@$\lambda$@ (+. $0 REAL)) $0) $1))))
#(@$\lambda$@ (#(@$\lambda$@ (+. $0 REAL)) (#(@$\lambda$@ (#(/. REAL) (#(@$\lambda$@ (+. $0 REAL)) $0))) $0)))
#(#(@$\lambda$@ (@$\lambda$@ (#(/. REAL) (/. (#(@$\lambda$@ (+. $0 REAL)) $0) $1)))) (#(@$\lambda$@ (/. (#(@$\lambda$@ (/. (/.  REAL $0) $0)) $0) $0)) REAL))
#(@$\lambda$@ (/. (#(@$\lambda$@ (#(@$\lambda$@ (#(@$\lambda$@ (+. $0 REAL)) (*. $0 REAL))) (*. (#(@$\lambda$@ (+. $0 REAL)) $0) $0))) $0) (#(@$\lambda$@ (+. $0 REAL)) $0)))
\end{lstlisting}
